Flexibility of interactions depends on habitat suitability

### 2019-09-02 paper/manuscript.Rmd
Continue attempt at intro P5

Here, we expli
Benadi found that

@@

Here we

Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling. However, one study of pollinator communities along an elevational gradient found that apparently specialized pollinators were facultatively more generalist than they appeared and could adapt their visitation patterns across sites as much as generalists to avoid phenological asynchrony (Benadi et al. 2014). Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza ́ lez- Castro et al. 2012), and a long-term study found no difference between specialist and generalist plant species in their interannual fluctuations in phenology and pollinator richness (Petanidou et al. 2014). Although these findings suggest that the facultative generalism of pollination mutualisms may confer robustness to these networks in the face of altered phenology (see also discussion on rewiring above), this robustness may depend on the climate context and the diversity and specialization within the network (Hoiss et al. 2015). Moreover, less-generalized interactions such as those between parasites and hosts may show less flexibility.

>>>>

Here we use information on plant-pollinator interactions and their environmental suitability at a global scale to test the stress/suitability hypotheses of

Here, we explicitly test 
Benadi found that

@@

Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling. However, one study of pollinator communities along an elevational gradient found that apparently specialized pollinators were facultatively more generalist than they appeared and could adapt their visitation patterns across sites as much as generalists to avoid phenological asynchrony (Benadi et al. 2014). Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza lez- Castro et al. 2012), and a long-term study found no difference between specialist and generalist plant species in their interannual fluctuations in phenology and pollinator richness (Petanidou et al. 2014). Although these findings suggest that the facultative generalism of pollination mutualisms may confer robustness to these networks in the face of altered phenology (see also discussion on rewiring above), this robustness may depend on the climate context and the diversity and specialization within the network (Hoiss et al. 2015). Moreover, less-generalized interactions such as those between parasites and hosts may show less flexibility.
